{\helveticaitalic{Supplementary Material}}: \\ \helvetica{Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB}

### 2018-07-11 paper/supplementary/supplementary.tex

\begin{enumerate}
	\item \cite{bronkRegulationEagCa22018}
	\item \cite{brookingsAutomaticParameterEstimation2014}
	\item \cite{caplanManyParameterSets2014a}
	\item \cite{dethierPositiveFeedbackCellular2015a}
	\item \cite{drionDopaminePacemakerNeuron2017}
	\item \cite{goldmanGlobalStructureRobustness2001a}
	\item \cite{herasModulationVoltagedependentConductances2018}
	\item \cite{kisperskyIncreaseSodiumConductance2012a}
	\item \cite{linActivityDependentAlternativeSplicing2012}
	\item \cite{liuModelNeuronActivityDependent1998}
	\item \cite{nadimFrequencyRegulationSlow1998}
	\item \cite{nadimSynapticDepressionCreates1999}
	\item \cite{odowdVoltageclampAnalysisSodium1988}
	\item \cite{prinzAlternativeHandtuningConductancebased2003a}
	\item \cite{rodriguezConvergentRhythmGeneration2013}
	\item \cite{sharpDynamicClampComputergenerated1993a}
	\item \cite{soto-trevinoActivitydependentModificationInhibitory2001}
	\item \cite{soto-trevinoComputationalModelElectrically2005a}
	\item \cite{swensenModulatorsConvergentCellular2001a}
	\item \cite{turrigianoSelectiveRegulationCurrent1995a}
	\item \cite{wicherNonsynapticIonChannels2001}
\end{enumerate}

>>>>

\begin{enumerate}
	\item EAGes, EAGmut, EAGwt (\cite{bronkRegulationEagCa22018})
	\item A-type (\cite{brookingsAutomaticParameterEstimation2014})
	\item MICurrent (\cite{caplanManyParameterSets2014a})
	\item CaT, H, Kd, NaV (\cite{dethierPositiveFeedbackCellular2015a})
	\item CaL, CaPump, KCa, Kd, NaV (\cite{drionDopaminePacemakerNeuron2017})
	\item Ap, At, Cal, KCa, KCaT, Proc (\cite{goldmanGlobalStructureRobustness2001a})
	\item Shaker (\cite{hardieNovelPotassiumChannels1991})
	\item Novel, Shab, Shaker (\cite{herasModulationVoltagedependentConductances2018})
	\item A-type, CaS, CaT, H, KCa, Kd, NaV (\cite{kisperskyIncreaseSodiumConductance2012a})
	\item NaP, NaT (\cite{linActivityDependentAlternativeSplicing2012})
	\item A-type, CaS, CaT, H, KCa, Kd, NaV (\cite{liuModelNeuronActivityDependent1998})
	\item \cite{liuModelNeuronActivityDependent1998} conductances with cached gating functions
	\item \cite{liuModelNeuronActivityDependent1998} conductances with forward Euler integration
	\item \cite{liuModelNeuronActivityDependent1998} conductances with temperature dependence
	\item Kd and NaV conductances from Int1, LG, and MCN1 cells (\cite{nadimFrequencyRegulationSlow1998})
	\item Cal (\cite{nadimSynapticDepressionCreates1999})
	\item Drosophila NaV (\cite{odowdVoltageclampAnalysisSodium1988})
	\item A-type, CaS, CaT, H, KCa, Kd, NaV (\cite{prinzAlternativeHandtuningConductancebased2003a})
	\item \cite{prinzAlternativeHandtuningConductancebased2003a} conductances with cached gating functions
	\item \cite{prinzAlternativeHandtuningConductancebased2003a} conductances with temperature dependence
	\item Kd and NaV from Int1 cells and modulatory input and transient LTS conductances from LG cells (\cite{rodriguezConvergentRhythmGeneration2013})
	\item proctolin modulatory input (\cite{sharpDynamicClampComputergenerated1993a})
	\item Cal and Kd from AB-PD, LP, and PY cells (\cite{soto-trevinoActivitydependentModificationInhibitory2001})
	\item A-type, CaT, and KCa from AB and PD cells, generic H, Kd, NaP, NaV, and proctolin conductances (\cite{soto-trevinoComputationalModelElectrically2005a})
	\item proctolin modulatory input (\cite{swensenModulatorsConvergentCellular2001a})
	\item A-type, CaS, CaT, H, KCa, Kd, NaP, NaV (\cite{turrigianoSelectiveRegulationCurrent1995a})
	\item Drosophila NaV (\cite{wicherNonsynapticIonChannels2001})
\end{enumerate}
